### 2007-09-26 Developer/eqPly/chapters/datastructure.tex
Updated /doc/Developer/eqPly.
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\begin{table}[ht]
\centering
\begin{tabular}{lrr}
\textbf{Modell} & \textbf{Dateigrösse Octree} & \textbf{Dateigrösse kd-Tree} \\
Armadillo & 27.72 MB & 6.09 MB \\
Dragon & 69.83 MB & 15.34 MB \\
Happy Buddha & 87.16 MB & 19.05 MB \\
Lucy & n/a & 494.58 MB \\
Stanford Bunny & 5.56 MB & 1.20 MB \\
\end{tabular}
\caption{Unterschied Speicherbedarf der Datenstrukturen}
\label{tbl:file-sizes}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
\textbf{Modell} & \textbf{Dateigrösse Octree} & \textbf{Dateigrösse kd-Tree} &
\textbf{Verhältnis}\\
Armadillo & 27.72 MB & 6.09 MB & 21.96 \%\\
Dragon & 69.83 MB & 15.34 MB & 21.97 \%\\
Happy Buddha & 87.16 MB & 19.05 MB & 21.86 \%\\
Lucy & n/a & 494.58 MB & n/a\\
Stanford Bunny & 5.56 MB & 1.20 MB & 21.56 \%\\
\end{tabular}
\caption{Unterschied Speicherbedarf der Datenstrukturen}
\label{tbl:file-sizes}
\end{table}
